\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-07-29 manuscript/main.tex
new file:   manuscript/July29.pdf 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

As our empirical results show, Lianjia's strategy has significantly enhanced its network strength within segmented markets. From this perspective, the enhancement of network effects further drives the market toward an oligopolistic competitive structure. Moreover, with the development of online platforms and new technologies, such as Lianjia's latest VR home viewing technology, these network effects are gradually shifting from local networks to a global network. As a result, this development is shaping the overall market into an oligopolistic competition model on a larger scale.

>>>>

In local segmented markets, oligopolistic firms are responsible for increasing network strength and have significant market power. In segmented markets where some oligopolistic firms do not have strong network effects, multiple other firms serve the diverse needs of consumers and expand their scale. The environment of free entry, rapid technological progress, and business model innovation leads to an inclusive competitive landscape in the real estate brokerage market. This environment allows oligopolistic firms to either enhance the strength of their network effects or have their dominant positions challenged. As a result, monopolistic structures emerge from and are subsequently disrupted by competition, allowing real estate intermediaries to continuously evolve and drive the industry's rapid growth. The practical implication is that a competitive oligopolistic structure does not inherently impede competitive efficiency. Instead, it can enhance firm efficiency, thereby facilitating better transactions for buyers and sellers and increasing overall market welfare.

As our empirical results show, Lianjia's strategy has significantly enhanced its network strength within segmented markets. From this perspective, the enhancement of network effects further drives the segmented market toward an oligopolistic competitive structure, which could increase the market welfare and facilitate the transactions between buyers and sellers. Moreover, with the development of online platforms and new technologies, such as Lianjia's latest VR home viewing technology, these network effects are gradually shifting from local networks to a global network. As a result, this development is shaping the overall market into an oligopolistic competition model on a larger scale.

In the future, as the network effects intensify, the real estate market may witness a more pronounced consolidation of market power among a few dominant players. This consolidation can lead to increased efficiencies through economies of scale and scope, where firms leverage their vast data resources and technological advancements to optimize operations and enhance consumer experiences. However, this shift also raises important considerations for regulatory bodies to ensure that the market remains competitive and accessible. The dynamic interplay between technological innovation and market structure will be crucial. As firms like Lianjia continue to innovate, incorporating artificial intelligence, big data analytics, and blockchain for secure transactions, the real estate market could become more transparent and efficient. These advancements could lower transaction costs, reduce information asymmetry, and provide consumers with more personalized services. Furthermore, the global reach of network effects implies that real estate markets across different regions might become more interconnected. This interconnectivity can facilitate cross-border investments and diversify property portfolios for investors, contributing to a more resilient global real estate market.

In conclusion, the evolution of the real estate market towards an oligopolistic competition model, driven by network effects and technological advancements, presents both opportunities and challenges. Policymakers and industry stakeholders must navigate this landscape carefully to harness the benefits of increased efficiency and innovation while safeguarding against potential market power abuses and ensuring equitable access for all participants. This balanced approach will be essential for sustaining long-term growth and enhancing overall market welfare in the real estate industry.
